### 2019-09-23 reports/paper1/paper.tex
Modify graphs to align and look better

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=1.05\textwidth, height=5.0cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logpBW.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMeanBW.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStdBW.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted white positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

>>>>

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sigBW.eps}
        \caption{X-ray projection with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logpBW.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMeanBW.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStdBW.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter, on each segment independently, with radius $r=\SI{130}{\pixel}$. a) X-ray projection with highlighted white positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

### 2019-09-23 reports/thesis/chapters/5_inference.tex
Modify graphs to align and look better

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \label{fig:inference_DefectSimulationDust_type1}
        \caption{Type 1 error}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated salt defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$. In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively. In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination. The filter used a kernel radius of \SI{20}{\pixel}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The boxplot summarise the 100 repeats of the experiment.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Obtained projection (\SI{}{\adu})}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}

>>>>

\begin{figure}
  \centering
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_roc.eps}
        \caption{AUC}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type1.eps}
        \caption{Type 1 error}
        \label{fig:inference_DefectSimulationDust_type1}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_type2.eps}
        \caption{Type 2 error}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectAltDustEmpirical_fdr.eps}
        \caption{FDR}
        \label{fig:inference_DefectSimulationDust_fdr}
      \end{subfigure}
    }
  \caption{AUC and various errors obtained when conducting hypotheses testing on an empirical null filtered contaminated salt defected Gaussian image of size $\SI{256}{\pixel} \times \SI{256}{\pixel}$. In a), the upper/lower dot dashed line shows the resulting mean AUC when testing on a defected image before/after contamination respectively. In b) c) d) the dashed lines shows the 95\% empirical confidence interval of the resulting error when testing the defected image before contamination. The filter used a kernel radius of \SI{20}{\pixel}. Defected pixels have the distribution $\normal(\mu_1,1)$ where $\mu_1$ was varied in this experiment. The salt defect has density $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}|H_{0,x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. The test was done at the 5\% FDR level. The boxplot summarise the 100 repeats of the experiment.}
  \label{fig:inference_DefectSimulationDust}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Obtained projection (\SI{}{\adu})}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}
